A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-06 paper.tex
starting Propose Method section

% intuitionistic interval
\begin{equation}
  0 \leq \mu_{A}(x) + \nu_{A}(x) \leq 1
\end{equation}

% every ordinary fuzzy set has the form
\begin{equation}
  \{ \langle x, \mu_{A}(x), 1 - \mu_{A}(x) \rangle | x \in E \}
\end{equation}

% if
\begin{equation}
  \pi_{A}(x) = 1 - \mu_{A}(x) - \nu_{A}(x)
\end{equation}

@@

How a classic fuzzy set is represented as a ifs. How an intuitionistic
fuzzy set is represented in this work.

How the non-membership is going to affect the membership (show
formula). Present both examples (stating the parameters).

How the coa is calculated (show formula and plot). How the formula can
be contracted.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs}
  \caption{An Example of an Intuitionistic Fuzzy Set}
  \label{ifs}
\end{figure}

>>>>

% intuitionistic interval
\begin{equation}
  \label{intuitionistic-interval}
  0 \leq \mu_{A}(x) + \nu_{A}(x) \leq 1
\end{equation}

% every ordinary fuzzy set has the form
\begin{equation}
  \label{ifs-form}
  \{ \langle x, \mu_{A}(x), 1 - \mu_{A}(x) \rangle | x \in E \}
\end{equation}

% if
\begin{equation}
  \label{fs-as-ifs-if}
  \pi_{A}(x) = 1 - \mu_{A}(x) - \nu_{A}(x)
\end{equation}

@@

The method, for now, consists on the procedures and elements
necessary to construct a basic Intuitionistic Fuzzy Inference System
(IFIS). This design was completed in order to make comparisons against
classic fuzzy inference systems, such as Type-1 FIS, Interval
Type-2 and General Type-2 FIS, and prove that
the design was viable and able to contribute to better results than
the classic FISs.

In many works, intuitionistic fuzzy sets (IFSs) are constructed by
hand, by interviewing experts who assign memberships and
non-memberships to each of the values of a set (such as in
\cite{davarzani2013novel}). This work proposes a convenient way of
creating an IFS, imitating many systems that use Gaussian
membership functions to facilitate an expert the representation of a
fuzzy interpretation. An example of an IFS is depicted in
Fig. \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
the membership function as the red line, and the non-membership
function as the blue line. In order to contruct the non-membership
function, one has to invert a normal Gaussian membership function.

Two convenient ways of modifying the non-membership function and
satisfy (\ref{intuitionistic-interval}) are as follows: 1) one can set
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the $height$ of the non-membership function,
as is depicted in \ref{ifs}; and 2) one can set different means and
standard deviations of the Gaussian membership and non-membership
functions, but the $height$ of the membership function must be equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. To clarify, the $height$
of the membership function ($h_{mf}$) of an IFS is equal to
$max(\mu(x))$, and the $height$ of the non-membership function
($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

%\ref{ifs-diff-mu-sd}

% How a classic fuzzy set is represented as a ifs. How an intuitionistic
% fuzzy set is represented in this work.

% How the non-membership is going to affect the membership (show
% formula). Present both examples (stating the parameters).

% How the coa is calculated (show formula and plot). How the formula can
% be contracted.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs}
  \caption{An Example of an Intuitionistic Fuzzy Set - Same Mean and SD}
  \label{ifs}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs-diff-mu-sd}
  \caption{An Example of an Intuitionistic Fuzzy Set - Different Mean
    and SD}
  \label{ifs-diff-mu-sd}
\end{figure}
